Geospatial Data Science - Final project

### 2025-03-26 final/archive/streamlined_nb.Rmd
Restructured, cleaned, added final code

---
title: "Geospatial Data Science - Final project"
author:
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
subtitle: Analysis of US road accidents and construction sites
output:
  html_notebook:
    df_print: paged
    toc: true
  html_document:
    toc: true
    df_print: paged
---

>>>>

---
title: "Geospatial Data Science - Final project"
author:
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
subtitle: Analysis of US road accidents and construction sites
output:
  html_document:
    toc: true
    df_print: paged
  html_notebook:
    df_print: paged
    toc: true
---
